Storing messages with multipartite neural cliques

### 2014-07-18 Articles/article.tex
...

	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal}$ which is the matrix where all edges between  activated units for each state $x$ in the same cluster have been added.
	$W$ can now be expressed as :\vspace*{1mm}

@@

  As taking a maximum is associative and commutative, storing can be done online and is independent of the order in which messages are stored.

@@

		We consider an altered version $\tilde{x}$ of a message $x$ which we are trying to retrieve. We set $\tilde{x}^0 = \tilde{x}$. The network is in state $\tilde{x}$ at the beginning of the retrieving. The message will be successfully retrieved if at the end of the algorithm, the network is in state $x$.

@@

	We first compute the theoretical density of the network, that is to mean the probability for a random edge $(l, l')$ to be present in the network (i.e. $W_{ll'} = 1$). We then express the theoretical error rate after one iteration of the retrieving rule in function of the density. All this computations (on error rates) are done assuming existences of edges between random units are independent, which is false but is a convenient approximation that gives results matching very closely results from simulations.

@@

	As the probability for $l$ and $l'$ to be active in their respective clusters for one message is $\frac{a}{l}$ providing messages are identically distributed, it follows that the probability for the edge $(l,l')$ of not being added in the network for one message is $1 - \left(a/l\right)^2$. Since messages are independent, the density $d$, which is the probability for an edge to be in the network, can be expressed as :

>>>>

	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal} = \bigvee_{x\in \mathcal{M}} x x^{\intercal}$ which is the matrix where all edges between  activated units for each state $x$ in the same cluster have been added.
	$W$ can now be expressed as :\vspace*{1mm}

@@

  As logical or ($\vee$) is associative and commutative, storing can be done online and is independent of the order in which messages are stored.

@@

		We consider an altered version $\tilde{x}$ of a message $x$ which we are trying to retrieve. We set $\tilde{x}^0 = \tilde{x}$. The network is in state $\tilde{x}$ at the beginning of the retrieving. The state of the network at the beginning of the step $t$ will be denoted by $\tilde{x}_t$. The message will be successfully retrieved if at the end of the algorithm, the network is in state $x$.

@@

	We first compute the theoretical density of the network, that is to mean the probability for a random edge $(i, i')$ to be present in the network (i.e. $W_{ii'} = 1$). We then express the theoretical error rate after one iteration of the retrieving rule in function of the density. All this computations (on error rates) are done assuming existences of edges between random units are independent, which is false but is a convenient approximation that gives results matching very closely results from simulations.

@@

	As the probability for $i$ (and $i'$) to be active in its cluster for one message $x$ is $\frac{a}{l}$ providing messages are uniformly distributed, it follows that the probability for the edge $(i,i')$ of not being added in the network for $x$ is $1 - \left(a/l\right)^2$. Since messages are independent, the density $d$, which is the probability for an edge to be in the network, can be expressed as :
